term papaer 2

### 2024-02-13 outputs/paper/paper.qmd
paper

title: "term paper 2"
author: "Hao Wang  Siqi Fei Xuecheng Gao"
thanks: "Code and data are available at: https://github.com/groundUofT888/Term-Paper-2.git ; Replication on Social Science Reproduction platform available at: www.aeaweb.org/articles?id=10.1257/app.20210529"
date: "February 12, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: " "
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes 
nocite: '@*'
bibliography: references.bib
---

@@

\blandscape

\elandscape

```{r, message=FALSE, message=FALSE, echo=FALSE, include=FALSE}
#| label: draft code (not used)

>>>>

title: "term paper 2" author: "Hao Wang Siqi Fei Xuecheng Gao" thanks: "Code and data are available at: https://github.com/groundUofT888/Term-Paper-2.git ; Replication on Social Science Reproduction platform available at: www.aeaweb.org/articles?id=10.1257/app.20210529" date: "February 12, 2024" date-format: long format: pdf: include-in-header: text: \|

```{=tex}
\usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
```
documentclass: article geometry: margin = 1in abstract: " " number-sections: true output: bookdown::pdf_document2 toc: false fig_caption: yes nocite: '@*' bibliography: references.bib ---

@@

```{=tex}
\begin{landscape}
```
```{=tex}
\end{landscape}
```
```{r, message=FALSE, message=FALSE, echo=FALSE, include=FALSE}
#| label: draft code (not used)
